# Results

```{r}
#load necessary packages
library(stringr) #for data cleaning
library(tidyverse) #for data cleaning
library(ggplot2) #for data visualization
library(ggridges) #to make histogram-like ridge plots
library(forcats) #for respecifying levels of a factor (i.e. the reorder() function)
library(ggrepel) #to separate the labels of outliers in a box and whisker plot
library("readr")
library("htmlwidgets")
library("GGally")
library("vcd")
library("readxl")
library("viridis")
library("RColorBrewer")
```

## Examination on Objective Coder Ratings

One major question of interest in this study was whether participant's self-reports of how stressed they would be in each scenario corresponds with objective coder ratings of the severity of those scenarios, as coded by the Daily Inventory of Stressful Events (DISE) scheme (Midus, 1994). A priori, we expected that participant ratings of the stressfulness of the events would correspond with the objective coders' ratings of the severity of the events. Both the subjective responses and the objective codes ranged from 0=not at all to 4=extremely. 

We were also interested in investing whether variance in subjective reports depended on the objective codes; for example, whether scenarios in the 2-3 range in objective severity were more variable while those in the high and low ranges of severity exhibited less variability. To explore these ideas, we build six histogram-style ridge plots, three for each session (session 1 or session 2 of the study) and one for each measure of stress (how 'stressed' did you feel? how 'overwhelmed' did you feel? and an aggregate score that is the mean of how 'stressed' and 'overwhelmed' participants felt). 

In the plots below, the x-axis is subjective ratings of stressed, overwhelmed, and the aggregate and the y-axis is the ID number for the vignettes. The y-axis is ordered such that vignettes at the top are the most objectively severe scenarios (4=extremely stressful) and decrease down the axis to the bottom, which contains vignettes rated as least objectively severe (0=not at all stressful). The objective severity of the scenarios is also color-coded, as depicted in a legend to the right of the plots. 

```{r, message=FALSE, results = FALSE}
#read in subjective ratings of vignettes
subj <- readRDS("Data/vignette_dat.RDS")

#take out participant 130 because two participant's have that ID...
el <- which(subj$ID == 130)
subj <- subj[-el,]

#separate into first and second session 
subj1 <- subj[which(subj$Session==1),]
subj2 <- subj[which(subj$Session==2),]

#SESSION 1
#subset and generate aggregate stressed score (aggregate of stressed and overwhelmed)
s1 <- subj1[grep("stressed", subj1$vignette),] #subset down to 'stressed'
s1$score <- as.numeric(s1$score) #change to numeric 
o1 <- subj1[grep("Overwhelmed", subj1$vignette),]  #subset down to 'overwhelmed'
o1$score <- as.numeric(o1$score) #change to numeric

subj1 <- s1 #begin process of combining
subj1$agg_stress <- rowMeans(cbind(s1$score, o1$score)) #combine scores

subj1$stressed <- s1$score #create 'clearer' variable for self reported stress
subj1$overwhelmed <- o1$score #create variable for overwhelmed

#read in objective codes of vignettes
obj <- read.csv("Data/objective codes.csv")
#subjset down to vignette ID's and objective codes
obj <- obj[,c(1,9)]
#relabel column headings
colnames(obj) <- c("vid", "severity")

#merge together so that the subjective file has the objective codes 
#create column with just vignette number in subjective file 
regexp <- "[[:digit:]]+" #prepare regular expression
subj1$vid <- as.numeric(str_extract(subj1$vignette, regexp)) #pull out numeric from the strings 

subj1 <- merge(subj1, obj, by = "vid", all.x=TRUE) #merge together

#order by objective severity
subj1 <- subj1[order(subj1$severity),] 
subj1$vid <- as.factor(subj1$vid)
subj1$vid <- fct_inorder(subj1$vid)

subj1$severity <- as.factor(subj1$severity) #change to class factor

#plot
#stressed
ggplot(subj1, aes(x = stressed, y = vid, fill = severity)) + 
  geom_density_ridges(stat="binline")+
  xlab("Subjective Stress")+
  ylab("Vignette ID")+
  labs(fill = "Objective Stress")+
  ggtitle("Session 1 - Stressed")+
  theme_ridges()+ theme(axis.text.y = element_text(size=5))+ theme(legend.position="bottom")

#overwhelmed 
ggplot(subj1, aes(x = overwhelmed, y = vid, fill = severity)) + 
  geom_density_ridges(stat="binline")+
  xlab("Subjective Stress")+
  ylab("Vignette ID")+
  labs(fill = "Objective Stress")+
  ggtitle("Session 1 - Overwhelmed")+
  theme_ridges()+ theme(axis.text.y = element_text(size=5))+ theme(legend.position="bottom")

#aggregate
ggplot(subj1, aes(x = agg_stress, y = vid, fill = severity)) + 
  geom_density_ridges(stat="binline")+
  xlab("Subjective Stress")+
  ylab("Vignette ID")+
  labs(fill = "Objective Stress")+
  ggtitle("Session 1 - Aggregate of Stressed and Overwhelmed")+
  theme_ridges()+ theme(axis.text.y = element_text(size=5))+ theme(legend.position="bottom")

#SESSION 2
#subset and generate aggregate stressed score (aggregate of stressed and overwhelmed)
s2 <- subj2[grep("stressed", subj2$vignette),] #subset down to 'stressed'
s2$score <- as.numeric(s2$score) #change to numeric 
o2 <- subj2[grep("Overwhelmed", subj2$vignette),]  #subset down to 'overwhelmed'
o2$score <- as.numeric(o2$score) #change to numeric

subj2 <- s2 #begin process of combining
subj2$agg_stress <- rowMeans(cbind(s2$score, o2$score)) #combine scores

subj2$stressed <- s2$score #create 'clearer' variable for self reported stress
subj2$overwhelmed <- o2$score #create variable for overwhelmed

#read in objective codes of vignettes
obj <- read.csv("Data/objective codes.csv")
#subjset down to vignette ID's and objective codes
obj <- obj[,c(1,9)]
#relabel column headings
colnames(obj) <- c("vid", "severity")

#merge together so that the subjective file has the objective codes 
#create column with just vignette number in subjective file 
regexp <- "[[:digit:]]+" #prepare regular expression
subj2$vid <- as.numeric(str_extract(subj2$vignette, regexp)) #pull out numeric from the strings 

subj2 <- merge(subj2, obj, by = "vid", all.x=TRUE) #merge together

#order by objective severity
subj2 <- subj2[order(subj2$severity),] 
subj2$vid <- as.factor(subj2$vid)
subj2$vid <- fct_inorder(subj2$vid)

subj2$severity <- as.factor(subj2$severity) #change to class factor

#plot
#stressed
ggplot(subj2, aes(x = stressed, y = vid, fill = severity)) + 
  geom_density_ridges(stat="binline")+
  xlab("Subjective Stress")+
  ylab("Vignette ID")+
  labs(fill = "Objective Stress")+
  ggtitle("Session 2 - Stressed")+
  theme_ridges()+ theme(axis.text.y = element_text(size=5))+ theme(legend.position="bottom")

#overwhelmed 
ggplot(subj2, aes(x = overwhelmed, y = vid, fill = severity)) + 
  geom_density_ridges(stat="binline")+ 
  xlab("Subjective Stress")+
  ylab("Vignette ID")+
  labs(fill = "Objective Stress")+
  ggtitle("Session 2 - Overwhelmed")+
  theme_ridges()+ theme(axis.text.y = element_text(size=5))+ theme(legend.position="bottom")

#aggregate
ggplot(subj2, aes(x = agg_stress, y = vid, fill = severity)) + 
  geom_density_ridges(stat="binline")+
  xlab("Subjective Stress")+
  ylab("Vignette ID")+
  labs(fill = "Objective Stress")+
  ggtitle("Session 2 - Aggregate of Stressed and Overwhelmed")+
  theme_ridges()+ theme(axis.text.y = element_text(size=5))+ theme(legend.position="bottom")
```

We have several key takeaways from these visualizations. All discussion refers to all three ways of operationalizing stress: how 'stressed', how 'overwhelmed', and the aggregate of 'stressed' and 'overwhelmed' that participants reported. 

First, we see that participants generally report that they would be less stressed than expected by the objective coding scheme; many participants rate scenarios that are objectively a '1' as a '0', those that are objectively a '2' as a '1', and so on. However, the under-reporting is most severe for the low-range objective stressors (the 1's and 2's). At the same time, we do see the expected general increase in mean subjective ratings of stress across the objective range, with more objectively severe stressors being rated as more subjectively stressors. 

Next, we observe less variability in the high and low ranges of the scale, particularly in the '0' range. This implies that participants generally perceive very non-severe and very severe stressors as consensually stressful (i.e. little disagreement about the stressfulness of these scenarios), while subjective interpretation and therefore variability emerges in the '2' and '3' range of the objective scale. We think this visualization does a nice job of laying out the correspondence between objetive coding of the stressors and subjective interpretations of them. 

## Stress Levels on Different Objective Coder Ratings (Severity Levels)

```{r include=FALSE}
#Read in Data
poms_dat <- readRDS("Data/poms_dat.RDS")
vignette_dat <- readRDS("Data/vignette_dat.RDS")
Baseline <- read.csv("Data/Baseline.csv")
Code = read_excel("Data/Coded Vignettes.xlsx", sheet = "Vignettes")

#Join
Baseline %>% mutate(relationship = (gsr_1 + gsr_2 + gsr_3 + gsr_4 + gsr_5 + gsr_6 + gsr_7 + gsr_8)/8) %>% 
  mutate(loneliness =  (ucla2 + ucla3 +ucla4+ucla7+ucla8+ucla11+ucla12+ucla13+ucla14+ucla17+ucla18 + 45 - (ucla1 +ucla5+ucla6+ucla9+ucla10+ucla15+ucla16+ucla19+ucla20))/20) %>%
  select(sid, sex_assignment, household_income, relationship,loneliness) -> family
colnames(family)[1] = "ID"
vignette_dat$ID <- as.character(vignette_dat$ID)
family$ID <- as.character(family$ID)
vignette_family <- left_join(vignette_dat, family, by = "ID")

#Data type
vignette_family$score <- as.numeric(vignette_family$score)
vignette_family$vignette <- as.character(vignette_family$vignette)
vignette_family$sex_assignment <- as.factor(vignette_family$sex_assignment)

#Remain only stressed and overwhelmed answer
Remain <- c()
for (i in seq(1,nrow(vignette_family))){
  if((str_detect(vignette_family$vignette[i], "stressed") == T) | (str_detect(vignette_family$vignette[i], "Overwhelmed") == T)){
    Remain[i] = 1
  }
  else{
    Remain[i] = 0
  }
}
vignette_family$remain <- Remain
vignette_family <- subset(vignette_family, vignette_family$remain == 1)

#string name processing
vignette_family$vignette  <- extract_numeric(vignette_family$vignette)
vignette_family$vignette <- as.character(vignette_family$vignette)

#unique record for each participant
vignette_family %>% group_by(ID, vignette) %>% mutate(Score = mean(score)) %>% ungroup() -> v_family
v_family <- v_family %>% distinct(ID , vignette,.keep_all = T)
v_family$sex_assignment <- as.character(v_family$sex_assignment)
v_family <- na.omit(v_family)
v_family$vignette <- as.character(v_family$vignette)
v_family$sex_assignment[v_family$sex_assignment == 1] <- "Female"
v_family$sex_assignment[v_family$sex_assignment == 0] <- "Male"

# cut continuouse number in levels
v_family$Relationship <- cut(v_family$relationship, 3, labels = c("not understanding","medium","close"))
v_family$Household_income <- cut(v_family$household_income,3, labels = c("low","medium","high"))
v_family %>% group_by(ID) %>% mutate(PeopleTotalScore = sum(Score)) %>% ungroup() -> v_family
v_family$PeopleTotalScoreF <- cut(v_family$PeopleTotalScore, 3, labels = c("relaxed","medium","stressed"))
v_family$Loneliness <- cut(v_family$loneliness, 3, labels = c("not_lonely", "medium", "lonely"))

#content of vignette
colnames(Code)[1] <- "vignette"
Code$vignette <- as.character(Code$vignette)
colnames(Code)[4] <- "content"
Code$content <- as.character(Code$content)
colnames(Code)[9] <- "severity"
Code$severity <- as.factor(Code$severity)
Code %>% select(vignette,content, severity) -> code_selected

code_selected$content[code_selected$content == 1] <- "Interpersonal Tension"
code_selected$content[code_selected$content == 2] <- "Work/Education"
code_selected$content[code_selected$content == 3] <- "Home"
code_selected$content[code_selected$content == 4] <- "Finances"
code_selected$content[code_selected$content == 5] <- "Health/Accident"
code_selected$content[code_selected$content == 6] <- "Discrimination"
code_selected$content[code_selected$content == 7] <- "Misc"

v_content <- left_join(v_family, code_selected, by = "vignette")
#v_content$father_education <- as.factor(v_content$father_education)
#v_content$mother_education <- as.factor(v_content$mother_education)
v_content$sex_assignment <- as.factor(v_content$sex_assignment)
v_content$score <- as.factor(v_content$score)
v_content$severity <-as.factor(v_content$severity)
v_content$Loneliness <- as.factor(v_content$Loneliness)

```

The vignettes are designed with different objective code ratings. The terminology "Objective Stress" represents how severe the potential consequence resulted from the conditions described in the vignettes may be.The Objective Stress is leveled into 4 levels, where 0 indicates the least severity and 4 stands for the most severity. Also, the vignettes are designed with different contents that are categorized into 7 categories: *Discrimination*,*Finances*,*Health/Accident*, *Home*, *Interpersonal Tension*, *Misc*, *Work/Education*. We want to see how people react with different contents in different level of Objective Stress.

```{r echo=FALSE}
colors = c('#EBF7E3',
          '#9BD770',
          '#66B032',
          '#375F1B',
          '#1B3409')
vcd::mosaic(score~ content,v_content, direction = c("v","h"),
           highlighting_fill = colors,rot_labels=c(15,0,0,0),gp_labels = gpar(fontsize = 7),labeling_args = list(set_varnames = c(score="Subjective Stress", content="Life Categories")),
            main = "Subjective Stress v.s. Life Categories")

v_content %>% group_by(score,content) %>% summarise(Counts = n()) %>% ungroup() %>%
ggplot(aes(x = content, y = Counts,fill =  score)) +
geom_bar(position = "dodge", stat = "identity",color = "#5D5F80") +
scale_fill_manual(values = c('#EBF7E3',
          '#9BD770',
          '#66B032',
          '#375F1B',
          '#1B3409')) + labs(title = "Subjective Stress v.s. Life Categories", x= "Life Categories", fill = "Subjtctive Stress")+ theme(legend.position="bottom")
```

The mosaic plots indicated that within the *Discrimination* and *Finance* categories, there are larger percentage of people with high level of stress. From the bar plot, under contents *Health/Accident*, *Home*, *Interpersonal Tension*, *Misc*, and *Work/Education*, the counts of the score presents an approximate descending order(score 0 counts most, score 4 counts last). However, for contents *Discrimination* and *Finance*, the counts of score is relatively even or in an ascending order, that is the reason why we can conclude that there are larger percentage of people with high level of stress within the *Discrimination* and *Finance* categories.

## Exploration on Individual Factors 
                                        
We also would like to see how people's baseline condition may have impacts on people's reaction to stress. We have *sex assignment*, *household income*, *loneliness*, *relationship with a people's close ones* these four factors selected. *sex assignment* is simply clustered as "Male" and "Female". Other three factors are separated in 3 levels respectively. By doing parallel coordinate graph, our goal is to see if clustering patterns exist for each factor. The parallel columns state for each vignette, ordered from most severe to least severe(left are those stressful conditions that may lead to the most severe consequence, and right are those that may lead to the least severe consequence). For each people's score, we averaged the scores from stressed level and overwhelmed level, then took the average of records from 2 sessions. From graphs below, the only clustering pattern we can see is from *sex assignment*. It shows that males are more likely to state that they are good at dealing with those conditions with higher severity.And overall, females present to be more stressed then males. Other three factors present no evident impact on people's reaction.

```{r echo=FALSE}
v_content %>% arrange(desc(severity)) %>%
  select(ID,Score,vignette,Household_income,sex_assignment,Relationship) %>%
  pivot_wider(names_from = vignette, values_from = Score) %>%
  ggparcoord(columns = (5:60),scale = "globalminmax", alpha = 0.5,groupColumn = "sex_assignment",splineFactor = 10) + 
  scale_color_manual(values = c("#A7414A","#6BAEFE")) + labs(title = "Grouped by Sex")+ theme(legend.position="bottom")+ theme(axis.text.x = element_text(size=5)) + labs(x = "ID", y = "Subjective Stress")

v_content %>% arrange(desc(severity)) %>%
  select(ID,Score,vignette,Household_income,Relationship,Loneliness) %>%
  pivot_wider(names_from = vignette, values_from = Score) %>%
  ggparcoord(columns = (5:60),scale = "globalminmax", alphaLines = 0.5,groupColumn = "Household_income",splineFactor = 10) + 
  scale_color_viridis(discrete=TRUE)+ labs(title = "Grouped by Household Income")+ theme(legend.position="bottom")+ theme(axis.text.x = element_text(size=5))+ labs(x = "ID", y = "Subjective Stress")

v_content %>% arrange(desc(severity)) %>%
  select(ID,Score,vignette,Household_income,Relationship,Loneliness) %>%
  pivot_wider(names_from = vignette, values_from = Score) %>%
  ggparcoord(columns = (5:60),scale = "globalminmax", alphaLines = 0.5, groupColumn = "Loneliness",splineFactor = 10) + 
  scale_color_viridis(discrete=TRUE)+ labs(title = "Grouped by Lonliness")+ theme(legend.position="bottom")+ theme(axis.text.x = element_text(size=5))+ labs(x = "ID", y = "Subjective Stress")

v_content %>% arrange(desc(severity)) %>%
  select(ID,Score,vignette,Household_income,Relationship,sex_assignment) %>%
  pivot_wider(names_from = vignette, values_from = Score) %>%
  ggparcoord(columns = (5:60),scale = "globalminmax", alphaLines = 0.5,groupColumn = "Relationship",splineFactor = 10) + 
  scale_color_viridis(discrete=TRUE)+ labs(title = "Relationship with Close Ones")+ theme(legend.position="bottom")+ theme(axis.text.x = element_text(size=5))+ labs(x = "ID", y = "Subjective Stress")

```

## Investigation on the relationship between Number of Siblings and Subjective Stress

To dive deep into what may cause the different levels of subjective stress, we decided to take a look at how the number of siblings may affect students' stress levels in different life categories. Since we have less than five percent of people with 4 or more siblings, we decided to conclude the data based on four categories, each with "0", "1","2","3+" siblings.

```{r}
subj <- readRDS("Data/vignette_dat.RDS")
el <- which(subj$ID == 130)
subj <- subj[-el,]
obj <- read.csv("Data/objective codes.csv")
obj <- obj[,c(1,3,4,9)]
colnames(obj) <- c("vid","broad","content","severity")
regexp <- "[[:digit:]]+"
subj$vid <- as.numeric(str_extract(subj$vignette, regexp))

subj <- merge(x = subj, y = obj, by = "vid", all.x = TRUE)
subj <- merge(x = subj, y = Baseline, by.x = "ID",by.y="sid", all.x = TRUE)
subj <- subj[,c(1,2,3,4,5,6,7,8,189)]
subj$sibling_age <- tolower(subj$sibling_age)
subj["sibling_count"] <- 0

subj$sibling_count <- str_count(subj$sibling_age, '\\d+')
#substract 'me','only child' as 1
subj$sibling_count<-ifelse(grepl('me', subj$sibling_age),subj$sibling_count-1,subj$sibling_count)
subj$sibling_count<-ifelse(grepl('only child', subj$sibling_age),0,subj$sibling_count)

subj$content[subj$content == 1] <- "Interpersonal Tension"
subj$content[subj$content == 2] <- "Work/Education"
subj$content[subj$content == 3] <- "Home"
subj$content[subj$content == 4] <- "Finances"
subj$content[subj$content == 5] <- "Health/Accident"
subj$content[subj$content == 6] <- "Discrimination"
subj$content[subj$content == 7] <- "Misc"

subj$score <- as.numeric(subj$score)
subj <- subj[!is.na(subj$content),]
subj <- subj[!is.na(subj$score),]
subj$sibling_count[is.na(subj$sibling_count)] <- 0
subj["sibnum"] <- ""
subj$sibnum<-ifelse(subj$sibling_count==0,"0",subj$sibnum)
subj$sibnum<-ifelse(subj$sibling_count==1,"1",subj$sibnum)
subj$sibnum<-ifelse(subj$sibling_count==2,"2",subj$sibnum)
subj$sibnum<-ifelse(subj$sibling_count>=3,"3+",subj$sibnum)

temp = subj %>% group_by(content,Session,sibnum)%>% mutate(Score = mean(score))

ggplot(temp, aes(x=factor(sibnum),y=Score,group=Session,colour=Session)) +geom_point()+geom_line()+facet_wrap(~content)+xlab("Number of Siblings")+ylab("Subjective Stress")+ggtitle("Subjective Stress vs. Number of Slibings, faceted by Life Categories")

```

Based on our graph, we could a few really interesting foundings:

1. Overall, we could observe a slight drop of stress level from Session 1 to Session 2, which may be caused by the time periods when the surveys were conducted. We also see an overall trend, where there is an increase of subjective stress when the the number of siblings increases from "1" to "2", and then an relatively bigger decline of subjective stress for students with 3+ siblings, especially on categories such that *Discrimination* and *Interpersonal Tension*. We suspect the reason behind this trend may be that students with more siblings receive less expectations from their parents, and they receive more love , support and care from all of their family members, where do not need to worry about finding new friends and they are more comfortable with themselves and less conscious of their beings. 

1. For scenarios with *Discrimination* problems, when number of siblings increase to 3 and more, we can see an apparent tendency that people start to feel less stress. We suspect that it may cause by the shared consciousness and understanding we own with more siblings.

2. For scenarios with *Interpersonal Tension* problem, we can see an extreme decline in the level of subjective stress when the number of siblings is more than 3. We suspect that this is due to the fact that students with more siblings may know better on how to communicate and negotiate with their friends since they have had their "practice" with their siblings, so they feel less stressed about it.

2. For scenarios with *Finances* problems, we thought there will be large increase of stress level for people have more siblings due to more family burden. However, there is actually a drop of stress level, especially for session 2. 

3. For scenarios with *Health/Accident* problems, we can see a clear decrease of stress level for both sessions when people have more siblings. We suspect that maybe this is because when you have more siblings, there will be more people care about your health problems and help you overcome any accidents, thus making people feel less stress.


## Potential Vignettes Outliers

We were also interested in visualizing the distribution of responses to the two questions asked for each scenario: 'have you experienced something like this before?' (1=yes) and 'was it easy to imagine yourself in this scenario?' (1=yes). We therefore calculated the proportion of participants who responded yes to each question and visualized a box and whisker plot of those proportions. We chose box and whisker plots because we are interested in finding outliers; in the next iteration of the study we will likely exclude scenarios that were extreme in terms of describing events that the sample hadn't experienced and being difficult to imagine oneself in the scenario.
```{r, message=FALSE, results = FALSE}
#read in subjective ratings of vignettes
subj <- readRDS("Data/vignette_dat.RDS")

#take out participant 130 because two participant's have that ID...
el <- which(subj$ID == 130)
subj <- subj[-el,]

#create column with just vignette number
regexp <- "[[:digit:]]+" #prepare regular expression
subj$vid <- as.numeric(str_extract(subj$vignette, regexp)) #pull out numeric from the strings 

#change score to character vector
subj$score <- as.numeric(subj$score)

#take out rows with NA
subj <- na.omit(subj)

#separate into first and second session 
subj1 <- subj[which(subj$Session==1),]
subj2 <- subj[which(subj$Session==2),]

#SESSION 1
#subset 
e11 <- subj1[grep("experience_1", subj1$vignette),] #subset down to experience 1 (I have experienced something like this before)
e12 <- subj1[grep("experience_2", subj1$vignette),] #subset down to experience 1 (It was easy to imagine myself in this situation)

# Experienced Something Like This Before
#get proportion yes per vignette
e11.l <- split(e11, e11$vid) #turn to a list
temp <- lapply(e11.l, function(x) sum(x$score)/nrow(x))
e11.prop <- as.data.frame(do.call("rbind", temp)) #turn into a data frame
e11.prop$vid <- as.numeric(names(e11.l)) #add back vignette ID
e11.prop$session <- "Session 1"

# Easy to Imagine Myself in this Situation
e12.l <- split(e12, e12$vid) #turn to a list
temp <- lapply(e12.l, function(x) sum(x$score)/nrow(x))
e12.prop <- as.data.frame(do.call("rbind", temp)) #turn into a data frame
e12.prop$vid <- as.numeric(names(e12.l)) #add back vignette ID
e12.prop$session <- "Session 1"

#SESSION 2
#subset 
e21 <- subj2[grep("experience_1", subj2$vignette),] #subset down to experience 1 (I have experienced something like this before)
e22 <- subj2[grep("experience_2", subj2$vignette),] #subset down to experience 1 (It was easy to imagine myself in this situation)

# Experienced Something Like This Before
#get proportion yes per vignette
e21.l <- split(e21, e21$vid) #turn to a list
temp <- lapply(e21.l, function(x) sum(x$score)/nrow(x))
e21.prop <- as.data.frame(do.call("rbind", temp)) #turn into a data frame
e21.prop$vid <- as.numeric(names(e21.l)) #add back vignette ID
e21.prop$session <- "Session 2"

# Easy to Imagine Myself in this Situation
e22.l <- split(e22, e22$vid) #turn to a list
temp <- lapply(e22.l, function(x) sum(x$score)/nrow(x))
e22.prop <- as.data.frame(do.call("rbind", temp)) #turn into a data frame
e22.prop$vid <- as.numeric(names(e22.l)) #add back vignette ID
e22.prop$session <- "Session 2"

# Combine
e1 <- rbind(e11.prop, e21.prop)
e2 <- rbind(e12.prop, e22.prop)

colnames(e1) <- c("proportion", "vid", "session")
colnames(e2) <- c("proportion", "vid", "session")

#set up code to label the outliers in the box and whisker plot
is_outlier <- function(x) {
  return(x < quantile(x, 0.25) - 1.5 * IQR(x) | x > quantile(x, 0.75) + 1.5 * IQR(x))
}

# Box & Whisker Plots
ggplot(e1, aes(x = session, y = proportion)) + 
  geom_boxplot() +
  coord_flip() +
  geom_text_repel(data = e1[is_outlier(e1$proportion),], aes(session, proportion, label = vid)) +
  ggtitle("Have you experienced something like this before?")+
  theme_classic()

ggplot(e2, aes(x = session, y = proportion)) + 
  geom_boxplot() +
  coord_flip() +
  geom_text_repel(data = e2[is_outlier(e2$proportion),], aes(session, proportion, label = vid)) +
  ggtitle("Was it easy to imagine yourself in this scenario?")+
  theme_classic()

```

These visualizations reveal several important things about the study. First, participants generally indicated that it was easy to imagine themselves in the scenarios (means for both session were above 90%), even though they hadn't necessarily been in situations exactly like them before (means for both sessions around 45%-50%). However, there were a few scenarios that participants found difficult to imagine: scenarios 165 and 48. In the next iteration of the study, we will likely remove these scenarios and replace them with situations that are more commonly experienced by undergraduate students.
