--- 
title: "Stress Perception Decomposition"
author: "Hongling Liu, Megan Goldring, Xinrui Zhang and Yuxin Zhou"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
---
```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
 
# Introduction

In today’s fast-paced modern world, stress has a profound impact on people’s psychological and physical functioning. Research on stress and the factors that cause it has therefore ballooned in since the 1970’s, when psychologists starting applying animal theories of stress to humans. It is now known that individual difference factors impact stress; for example the same stressor will have a greater impact on neurotic relative to non-neurotic people. Research has also shown that stressor factors impact stress; for example interpersonal stressors are generally more stressful than work stressors. Finally, it has been shown that idiosyncratic factors of person and stressor impact stress; for example some people are always more stressed by home-based stressors while others are always more stressed by financial stressors. 

Despite these advances in stress science, little is known about the relative importance of each of these factors. The main purpose of the study is therefore to conduct a crossed random effects model in order to decompose variability in stress responses into person, stressor, and person by stressor components. To do so, we asked multiple people to provide ratings of how ‘stressed’ and ‘overwhelmed’ they would be to each of 60 vignettes designed to range in ‘objective’ coder-rated stress. 

Although the crossed random effect model is not part of our project for this class, we conducted exploratory visualization analyses to provide preliminary insight into key aspects of the study. Our main goals were to investigate 1) whether people’s subjective stress responses align with objective coder ratings of how severe those scenarios were, 2) whether the area of life that an event occurs in (i.e. work or home) influences people’s subjective stress responses, 3) reveal the importance of individual factors such as sex and income that may influence stress responses, 4) investigate whether there was systematic bias between the 1st and 2nd instance of the study (all participants responded twice one week apart—see Data Sources section) as well as the importance of siblings in stress, and 4) identify problematic vignettes (i.e. those that participants being hard to imagine themselves in).

Together, we utilized lessons learned in class, including a targeted application of ridge plots, an insightful visualization with a mosaic plot, an exploratory use of parallel coordinate plots, and a practical application of box and whisker plots. We also made use of lessons on interactive data visualization by generating stacked bar charts to provide more flexibility for understanding one of our primary questions. 


<!--chapter:end:index.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Data sources

This data comes from a study designed and run by Megan, who is also a PhD student in the Psychology Department. We confirmed with Professor Robbins that using this dataset is appropriate for the EDAV course. In the study, multiple people to provides ratings of how ‘stressed’ and ‘overwhelmed’ they would be in each of 60 vignettes designed to range in ‘objective’ stress. 

In generating the vignettes of stressful events, we used the Daily Inventory of Stressful Events coding scheme. This scheme trains objective coders to rate each vignette. Two coders were trained and rated each vignette according to the DISE scheme; specifically how ‘objectively’ severe the stressor is from 0=not at all to 4=extremely, the life domain that the stressor falls into (i.e. home, work, etc), whether the stressor was chronic, whether it was a continuation of a stressor from a previous day, and whether the focus of involvement for the stressor was the self or someone else (i.e. a close family member).

To collect the data, 157 undergraduate students at Columbia participated for course credit. The study took place in 3 parts: 1) a 15-minute pre-study baseline survey, 2) study session one, and 3) study session two. The baseline survey assessed relevant psychological constructs such as loneliness, chronic stress experiences, and stress mindsets, in addition to demographic variables such as participant year in school, race, family income, etc. The second part consisted of meeting a trained research assistant online via Zoom. Participants first provided informed consent, then completed 3 brief mood questionnaires (Profile of Mood States; assessing current mood, mood during COVID, and mood in general in their life), followed by responding to each of the 60 vignettes. Upon hearing the research assistant read each vignette out loud, participants indicated: 1) how ‘stressed’ they would be from 0=not at all to 4=extremely, 2) how ‘overwhelmed’ they would be from 0=not at all to 4= extremely, 3) whether they had experienced something like the event described in the vignette with 1=yes and 0=no 4) whether it was easy to imagine themselves in the scenario described in the vignette with 1=yes and 0= no.

All data was therefore collected online via Qualtrics and it is all self-report survey data. The different data files contain different types of variables; either between-stressor measures of the vignettes (i.e. the objective codes), between-person measures of psychological traits and demographics (i.e. baseline data), or within-person stressor measures (i.e. the session 1 and session 2 data).

Due to the nature of the study (i.e. Columbia students filling out the surveys for course credit), there is very little missingness and few errors. The only errors that we did find (and not resolve!) was that three of the vignettes had more questions than they were supposed to. We opted to simply remove those vignettes from analysis for the purpose of this project.


<!--chapter:end:02-data.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Data transformation

There are four datafiles that we are working with: the objective code data file, the baseline data file, the mood measure data file (contains both session’s worth of data), and the vignette data file (also contains both session’s worth of data). 

We cleaned the baseline data in excel prior to inputting it in R; there are only a few “clean ups” that needed to happen: 1) eliminate rows 2 and 3 that contained meta data about the survey, 2) eliminate columns 2-15 because they contained irrelevant variables (i.e. longitude and latitude at which the survey was taken), and 3) eliminate the column with participant birthdays, as this is personally identifiable information and we only received IRB approval to disseminate and post completely anonymized data. 

The experimental data sessions were a little trickier. In order to partially randomize the order of the vignettes, participants were a priori randomly assigned to one of ten conditions, where all conditions contained the exact same vignettes but in a different order.  Therefore, the structure of each of these datasets is the same first few columns (those obtaining informed consent and the mood measures) followed by the vignette questions that were in different orders depending on the datafile. Because of this, we had to read in 10 separate datafiles, restructure them, and merge them. The codes are linked as below:

https://github.com/graceliudata/Stress-Perception-Decomposition/blob/main/Data/Transformation.Rmd



<!--chapter:end:03-cleaning.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Missing Values

```{r}
library(readr)
library(questionr)
library(ggplot2)
library(tidyr)
library(scales)
library(tibble)
library(forcats)
library(dplyr)
```

```{r}
poms_dat <- readRDS("Data/poms_dat.RDS")
vignette_dat <- readRDS("Data/vignette_dat.RDS")
Baseline <- read_csv("Data/Baseline.csv")
```

Our data missing analysis involves 3 data sets: Mood data, Vignette data, and Baseline data. For all visualizations, we confirmed that they are suitible for all types of color blindess: protanomaly, deuteranomaly, tritanomaly, protanopia, deuteranopia, tritanopia, and blue cone monochromacy to effectively read the graph. We confirmed that the visual is accessible to these individuals by plugging our images into https://www.color-blindness.com/coblis-color-blindness-simulator/ and looking at it in all color blind modes.

## Mood Data 
There were no missing values for the mood data
```{r}
freq.na(poms_dat) 
```

## Vignette Data 
There were also no missing values for the vignette data.
```{r}
freq.na(vignette_dat)
```

## Baseline Data
Baseline data did have some values missing.
For column patterns, we can see that the top 3 variables have the most missing data: 'non_heteronormative_3_TEXT', 'gender_idetity_5_TEXT' and 'race_12_TEXT'
This is quite reasonable since these variables are used to store the explanation part if people choose the 'other' option for variable 'non_heteronormative', 'gender_idetity' and 'race', respectively. Therefore, the reason why these 3 columns has leading missing values is people choose common options but rarely the 'other' option for 'non_heteronormative', 'gender_idetity' and 'race' variables.

```{r}
head(freq.na(Baseline),20)
```

For row patterns, with each row represents a student survey results, we found that there were 17 out of 201 students that only fill out a few of survey question and then quit. In fact, we decide to remove those who did not fill out at least 75% of the survey for data cleaning.
```{r}
rowSums(is.na(Baseline))
```

Here is a heatmap for row/column missing pattern, where x-axis for columns (survey questions), y-axis for row index (id for students)
1.While yellow cells indicates missing data, we can see patterns of 3 vertical yellow lines (top 3 variables with missing values) and 17 horizontal yellow lines (17 students miss more than 75% questions)
2.There is another pattern that students with id 31-73 have missing values for variable father_education and mother_education.

```{r}
myBaseline <- Baseline %>% rownames_to_column("id") %>% gather(key,value,-id,-sid) %>% mutate(key = factor(key)) %>% group_by(key) %>% ungroup()
myBaseline$missing <- ifelse(is.na(myBaseline$value),"yes","no")
colors <- c("#330066","#FFCC00")
myBaseline$id <- factor(myBaseline$id, levels = unique(myBaseline$id))
ggplot(myBaseline, aes(x = key, y = fct_rev(id))) + geom_tile(aes(fill = missing),color="gray")+scale_fill_manual(values=colors)+ ggtitle("Baseline Missing Data")+ theme(axis.text.x = element_text(angle = 90,vjust=0.5, hjust=1,size=5),axis.text.y = element_text(size=3))+ylab("Student ID")+xlab("Column Variables for Baseline") +theme(legend.position="bottom")
```

<!--chapter:end:04-missing.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Results

```{r}
#load necessary packages
library(stringr) #for data cleaning
library(tidyverse) #for data cleaning
library(ggplot2) #for data visualization
library(ggridges) #to make histogram-like ridge plots
library(forcats) #for respecifying levels of a factor (i.e. the reorder() function)
library(ggrepel) #to separate the labels of outliers in a box and whisker plot
library("readr")
library("htmlwidgets")
library("GGally")
library("vcd")
library("readxl")
library("RColorBrewer")
```

## Examination of Subjective Relative to Objective Stress

One major question of interest in this study was whether participant's self-reports of how stressed they would be in each scenario corresponds with objective coder ratings of the severity of those scenarios, as coded by the Daily Inventory of Stressful Events (DISE) scheme (Midus, 1994). A priori, we expected that participant ratings of the stressfulness of the events would correspond with the objective coders' ratings of the severity of the events. Both the subjective responses and the objective codes ranged from 0=not at all to 4=extremely. 

We were also interested in investing whether variance in subjective reports depended on the objective codes; for example, whether scenarios in the 2-3 range in objective severity were more variable while those in the high and low ranges of severity exhibited less variability. To explore these ideas, we build six histogram-style ridge plots, three for each session (session 1 or session 2 of the study) and one for each measure of stress (how 'stressed' did you feel? how 'overwhelmed' did you feel?) plus an aggregate score that is the mean of how 'stressed' and 'overwhelmed' participants felt they would be. 

In the plots below, the x-axis is subjective ratings of stressed, overwhelmed, and the aggregate and the y-axis is the ID number for the vignettes. The y-axis is ordered such that vignettes at the top are the most objectively severe scenarios (4=extremely stressful) and decrease down the axis to the bottom, which contains vignettes rated as least objectively severe (0=not at all stressful). The objective severity of the scenarios is also color-coded, as depicted in a legend to the right of the plots. 

Note that we also ensured that our visualization would allow individuals with protanomaly, deuteranomaly, tritanomaly, protanopia, deuteranopia, tritanopia, and blue cone monochromacy to effectively read the graph. We confirmed that the visual is accessible to these individuals by plugging our images into https://www.color-blindness.com/coblis-color-blindness-simulator/ and looking at it in all color blind modes. Although the color palette is not the prettiest, it is one that is accessible to all types of color blindness other than monochromacy because there is no way to use a colored visualization that will work for individuals with that kind of color blindness. In sum, we developed our own color palette that is as inclusive as possible.

```{r, message=FALSE, results = FALSE}
#read in subjective ratings of vignettes
subj <- readRDS("Data/vignette_dat.RDS")

#take out participant 130 because two participant's have that ID...
el <- which(subj$ID == 130)
subj <- subj[-el,]

#separate into first and second session 
subj1 <- subj[which(subj$Session==1),]
subj2 <- subj[which(subj$Session==2),]

#SESSION 1
#subset and generate aggregate stressed score (aggregate of stressed and overwhelmed)
s1 <- subj1[grep("stressed", subj1$vignette),] #subset down to 'stressed'
s1$score <- as.numeric(s1$score) #change to numeric 
o1 <- subj1[grep("Overwhelmed", subj1$vignette),]  #subset down to 'overwhelmed'
o1$score <- as.numeric(o1$score) #change to numeric

subj1 <- s1 #begin process of combining
subj1$agg_stress <- rowMeans(cbind(s1$score, o1$score)) #combine scores

subj1$stressed <- s1$score #create 'clearer' variable for self reported stress
subj1$overwhelmed <- o1$score #create variable for overwhelmed

#read in objective codes of vignettes
obj <- read.csv("Data/objective codes.csv")
#subjset down to vignette ID's and objective codes
obj <- obj[,c(1,9)]
#relabel column headings
colnames(obj) <- c("vid", "severity")

#merge together so that the subjective file has the objective codes 
#create column with just vignette number in subjective file 
regexp <- "[[:digit:]]+" #prepare regular expression
subj1$vid <- as.numeric(str_extract(subj1$vignette, regexp)) #pull out numeric from the strings 

subj1 <- merge(subj1, obj, by = "vid", all.x=TRUE) #merge together

#order by objective severity
subj1 <- subj1[order(subj1$severity),] 
subj1$vid <- as.factor(subj1$vid)
subj1$vid <- fct_inorder(subj1$vid)

subj1$severity <- as.factor(subj1$severity) #change to class factor

#plot
#stressed
ggplot(subj1, aes(x = stressed, y = vid, fill = severity)) + 
  geom_density_ridges(stat="binline")+
  ggtitle("Session 1 - Stressed")+
  xlab("Subjective Stress")+
  ylab("Vignette ID")+
  labs(fill = "Objective Stress")+
  scale_fill_manual(values=c("cadetblue3", "khaki", "mediumorchid2", "snow4","springgreen4", "saddlebrown"))+
  theme_ridges(center = TRUE)+ theme(axis.text.y = element_text(size=5))+ theme(legend.position="bottom")

#overwhelmed 
ggplot(subj1, aes(x = overwhelmed, y = vid, fill = severity)) + 
  geom_density_ridges(stat="binline")+
  ggtitle("Session 1 - Overwhelmed")+
  xlab("Subjective Overwhelmed")+
  ylab("Vignette ID")+
  labs(fill = "Objective Stress")+
  scale_fill_manual(values=c("cadetblue3", "khaki", "mediumorchid2", "snow4","springgreen4", "saddlebrown"))+
  theme_ridges(center = TRUE)+ theme(axis.text.y = element_text(size=5))+ theme(legend.position="bottom")

#aggregate
ggplot(subj1, aes(x = agg_stress, y = vid, fill = severity)) + 
  geom_density_ridges(stat="binline")+
  ggtitle("Session 1 - Aggregate Stressed and Overwhelmed")+
  xlab("Subjective Stress")+
  ylab("Vignette ID")+
  labs(fill = "Objective Stress")+
  scale_fill_manual(values=c("cadetblue3", "khaki", "mediumorchid2", "snow4","springgreen4", "saddlebrown"))+
  theme_ridges(center = TRUE)+ theme(axis.text.y = element_text(size=5))+ theme(legend.position="bottom")

#SESSION 2
#subset and generate aggregate stressed score (aggregate of stressed and overwhelmed)
s2 <- subj2[grep("stressed", subj2$vignette),] #subset down to 'stressed'
s2$score <- as.numeric(s2$score) #change to numeric 
o2 <- subj2[grep("Overwhelmed", subj2$vignette),]  #subset down to 'overwhelmed'
o2$score <- as.numeric(o2$score) #change to numeric

subj2 <- s2 #begin process of combining
subj2$agg_stress <- rowMeans(cbind(s2$score, o2$score)) #combine scores

subj2$stressed <- s2$score #create 'clearer' variable for self reported stress
subj2$overwhelmed <- o2$score #create variable for overwhelmed

#read in objective codes of vignettes
obj <- read.csv("Data/objective codes.csv")
#subjset down to vignette ID's and objective codes
obj <- obj[,c(1,9)]
#relabel column headings
colnames(obj) <- c("vid", "severity")

#merge together so that the subjective file has the objective codes 
#create column with just vignette number in subjective file 
regexp <- "[[:digit:]]+" #prepare regular expression
subj2$vid <- as.numeric(str_extract(subj2$vignette, regexp)) #pull out numeric from the strings 

subj2 <- merge(subj2, obj, by = "vid", all.x=TRUE) #merge together

#order by objective severity
subj2 <- subj2[order(subj2$severity),] 
subj2$vid <- as.factor(subj2$vid)
subj2$vid <- fct_inorder(subj2$vid)

subj2$severity <- as.factor(subj2$severity) #change to class factor

#plot
#stressed
ggplot(subj2, aes(x = stressed, y = vid, fill = severity)) + 
  geom_density_ridges(stat="binline")+
  ggtitle("Session 2 - Stressed")+
  xlab("Subjective Stress")+
  ylab("Vignette ID")+
  labs(fill = "Objective Stress")+
  scale_fill_manual(values=c("cadetblue3", "khaki", "mediumorchid2", "snow4","springgreen4", "saddlebrown"))+
  theme_ridges(center = TRUE)+ theme(axis.text.y = element_text(size=5))+ theme(legend.position="bottom")

#overwhelmed 
ggplot(subj2, aes(x = overwhelmed, y = vid, fill = severity))+ 
  geom_density_ridges(stat="binline")+
  ggtitle("Session 2 - Overwhelmed")+
  xlab("Subjective Stress")+
  ylab("Vignette ID")+
  labs(fill = "Objective Stress")+
  scale_fill_manual(values=c("cadetblue3", "khaki", "mediumorchid2", "snow4","springgreen4", "saddlebrown"))+
  theme_ridges(center = TRUE)+ theme(axis.text.y = element_text(size=5))+ theme(legend.position="bottom")

#aggregate
ggplot(subj2, aes(x = agg_stress, y = vid, fill = severity)) + 
  geom_density_ridges(stat="binline")+
  ggtitle("Session 2 - Aggregate Stressed and Overwhelmed")+
  xlab("Subjective Stress")+
  ylab("Vignette ID")+
  labs(fill = "Objective Stress")+
  scale_fill_manual(values=c("cadetblue3", "khaki", "mediumorchid2", "snow4","springgreen4", "saddlebrown"))+
  theme_ridges(center = TRUE)+ theme(axis.text.y = element_text(size=5))+ theme(legend.position="bottom")
```

We have several key takeaways from these visualizations. All discussion refers to all three ways of operationalizing stress: how 'stressed', how 'overwhelmed', and the aggregate of how 'stressed' and 'overwhelmed' reported by the participants. 

First, we see that participants generally report that they would be less stressed than expected by the objective coding scheme; many participants rate scenarios that are objectively a '1' as a '0', those that are objectively a '2' as a '1', and so on. However, the under-reporting is most severe for the low-range objective stressors (the 1's and 2's). At the same time, we do see the expected general increase in mean subjective ratings of stress across the objective range, with more objectively severe stressors being rated as more subjectively stressors. 

Next, we observe less variability in the high and low ranges of the scale, particularly in the '0' range. This implies that participants generally perceive very non-severe and very severe stressors as consensually stressful (i.e. little disagreement about the stressfulness of these scenarios), while subjective interpretation and therefore variability emerges in the '2' and '3' range of the objective scale. We think this visualization does a nice job of laying out the correspondence between objetive coding of the stressors and subjective interpretations of them. 

## Subjective Stress for Different Life Domains
```{r include=FALSE}
#Data setup block
#NOTE THAT THE CODE SETUP HERE IS NECESSARY FOR BOTH THIS CODE CHUNK AND THE ONE THAT FOLLOWS. We put together the dataset in a way that whill work for both visualizations, the  mosaic and the parallel coordinate plots. 

#read in data 
poms_dat <- readRDS("Data/poms_dat.RDS")
vignette_dat <- readRDS("Data/vignette_dat.RDS")
Baseline <- read.csv("Data/Baseline.csv")
Code = read_excel("Data/Coded Vignettes.xlsx", sheet = "Vignettes")

#Join baseline data with vignette data. Also, generate composite scores for relationships with close ones (gsr) and loneliness (ucla).
Baseline %>% mutate(relationship = (gsr_1 + gsr_2 + gsr_3 + gsr_4 + gsr_5 + gsr_6 + gsr_7 + gsr_8)/8) %>% 
  mutate(loneliness =  (ucla2 + ucla3 +ucla4+ucla7+ucla8+ucla11+ucla12+ucla13+ucla14+ucla17+ucla18 + 45 - (ucla1 +ucla5+ucla6+ucla9+ucla10+ucla15+ucla16+ucla19+ucla20))/20) %>%
  select(sid, sex_assignment, household_income, relationship,loneliness) -> family
colnames(family)[1] = "ID"
vignette_dat$ID <- as.character(vignette_dat$ID)
family$ID <- as.character(family$ID)
vignette_family <- left_join(vignette_dat, family, by = "ID")

#Change data types to what is needed in ggplot
vignette_family$score <- as.numeric(vignette_family$score)
vignette_family$vignette <- as.character(vignette_family$vignette)
vignette_family$sex_assignment <- as.factor(vignette_family$sex_assignment)

#Subset to the stressed and overwhelmed responses (for use in the plot below)
Remain <- c()
for (i in seq(1,nrow(vignette_family))){
  if((str_detect(vignette_family$vignette[i], "stressed") == T) | (str_detect(vignette_family$vignette[i], "Overwhelmed") == T)){
    Remain[i] = 1
  }
  else{
    Remain[i] = 0
  }
}
vignette_family$remain <- Remain
vignette_family <- subset(vignette_family, vignette_family$remain == 1)

#string name processing
vignette_family$vignette  <- extract_numeric(vignette_family$vignette) #get vignette id's
vignette_family$vignette <- as.character(vignette_family$vignette) #turn vignette id's to character

#generate a unique record for each participant
vignette_family %>% group_by(ID, vignette) %>% mutate(Score = mean(score)) %>% ungroup() -> v_family
v_family <- v_family %>% distinct(ID , vignette,.keep_all = T)
v_family$sex_assignment <- as.character(v_family$sex_assignment)
v_family <- na.omit(v_family)
v_family$vignette <- as.character(v_family$vignette)
v_family$sex_assignment[v_family$sex_assignment == 1] <- "Female"
v_family$sex_assignment[v_family$sex_assignment == 0] <- "Male"

# separate continuouse variables into categorical variables (for coloring the parallel coordinates plot below)
v_family$Relationship <- cut(v_family$relationship, 3, labels = c("not understanding","medium","close"))
v_family$Household_income <- cut(v_family$household_income,3, labels = c("low","medium","high"))
v_family %>% group_by(ID) %>% mutate(PeopleTotalScore = sum(Score)) %>% ungroup() -> v_family
v_family$PeopleTotalScoreF <- cut(v_family$PeopleTotalScore, 3, labels = c("relaxed","medium","stressed"))
v_family$Loneliness <- cut(v_family$loneliness, 3, labels = c("not_lonely", "medium", "lonely"))

#label life domains of the vignettes
colnames(Code)[1] <- "vignette"
Code$vignette <- as.character(Code$vignette)
colnames(Code)[4] <- "domain"
Code$domain <- as.character(Code$domain)
colnames(Code)[9] <- "severity"
Code$severity <- as.factor(Code$severity)
Code %>% select(vignette,domain, severity) -> code_selected

code_selected$domain[code_selected$domain == 1] <- "Interpersonal Tension"
code_selected$domain[code_selected$domain == 2] <- "Work/Education"
code_selected$domain[code_selected$domain == 3] <- "Home"
code_selected$domain[code_selected$domain == 4] <- "Finances"
code_selected$domain[code_selected$domain == 5] <- "Health/Accident"
code_selected$domain[code_selected$domain == 6] <- "Discrimination"
code_selected$domain[code_selected$domain == 7] <- "Misc"

v_domain <- left_join(v_family, code_selected, by = "vignette")
#v_domain$father_education <- as.factor(v_domain$father_education)
#v_domain$mother_education <- as.factor(v_domain$mother_education)
v_domain$sex_assignment <- as.factor(v_domain$sex_assignment)
v_domain$score <- as.factor(v_domain$score)
v_domain$severity <-as.factor(v_domain$severity)
v_domain$Loneliness <- as.factor(v_domain$Loneliness)

```

Another primary question was whether different life domains elicit relatively more or less stress. As coded by the two objective DISE coders, there were seven life domains: Discrimination events, Financial events, Interpersonal Tesnsion events, Work/Education events, Health/Accident Events, and Miscellaneous events. We chose to make a mosaic plot so that we could see the propotion of events in each domain as well as the relative amount of stress in each domain. 

Once again, we ensured that these visualizations were color-blind accessible. However, this time we simply used different shades of green and plugged the mosaic into the color blind website sited above and ensured that individuals with all types of color blindness could read them. 

```{r echo=FALSE}
colors = c('#EBF7E3',
          '#9BD770',
          '#66B032',
          '#375F1B',
          '#1B3409')
vcd::mosaic(score~ domain,v_domain, direction = c("v","h"),
           highlighting_fill = colors,rot_labels=c(15,0,0,0),gp_labels = gpar(fontsize = 7),labeling_args = list(set_varnames = c(score="Subjective Stress", domain="Life Domains")),
            main = "Subjective Stress vs. Life Domains")
```

The mosaic plot reveals several interesting trends. First, we see that there were relatively more work/education types of vignettes than the others. The least common type of vignette were the health/accident event. More interestingly, we can see that interpersonal tensions were the least stressful of all life domains, which is suprising given that prior work in this area has found interpersonal tensions to be the most, rather than least, stressful. We also see that financial events were deemed the most stressful. This may reflect the fact that the study was conducted during the COVID-19 pandemic, when financial sensitivity was high. It might also reflect the fact that most Columbia undergraduates are either relatively wealthy or relatively unwealthy (i.e. on scholarships) relative to the general population. These two types of financial circumstances might make financial stressors particularly problematic, as wealthy students would be concerned about their life changing to due to financial stressors (i.e one vignette descibes a call from a parent in which most family money as been lost) and unwealthy students might be particularly sensitive to dealing with financial hardships. It is also interesting to see that the discrimination scenarios were relativly well distributed. It might be that students who have experienced these types of events consider them to more or less stressful relative to students who have never experienced these types of events. With no a priori hypothesis, this is something that will be investigated in the formal analysis of this data. 

## Subjective Stress and Individual Difference Factors 
                                        
Next, we investigate how people's baseline condition may impact their reactions to stressors. Data was collected on *sex assignment*, *household income*, *loneliness*, and *relationship with a people's close ones*. Our goal was to use parallel coordinate plots to investigate clustering patterns for each individual difference factor. *Sex assignment* is simply clustered as "Male" and "Female". The other three factors are separated in 3 levels. In these graphs, the parallel axes are ordered from objectively most severe to objectively least severe (i.e. those events rated as most stressful by the DISE coders are on the left, descending to the least stressful rated by objective coders on the right). For subjective stress, we averaged the scores from self reported 'stressed' and self reported 'overwhelmed'. Once again, we used color-blind appropriate colors using the color palette we designed ourselves.

```{r echo=FALSE}
v_domain %>% arrange(desc(severity)) %>%
  select(ID,Score,vignette,Household_income,sex_assignment,Relationship) %>%
  pivot_wider(names_from = vignette, values_from = Score) %>%
  ggparcoord(columns = (5:60),scale = "globalminmax", alpha = 0.5,groupColumn = "sex_assignment",splineFactor = 10) + 
  scale_color_manual(values = c("cadetblue3", "mediumorchid2")) + labs(title = "Grouped by Sex")+ theme(legend.position="bottom")+ theme(axis.text.x = element_text(size=5)) + labs(x = "Vignette ID - Ordered from Most to Least Objectively Stressful", y = "Subjective Stress")

v_domain %>% arrange(desc(severity)) %>%
  select(ID,Score,vignette,Household_income,Relationship,Loneliness) %>%
  pivot_wider(names_from = vignette, values_from = Score) %>%
  ggparcoord(columns = (5:60),scale = "globalminmax", alphaLines = 0.5,groupColumn = "Household_income",splineFactor = 10) + 
  scale_color_manual(values = c("cadetblue3", "mediumorchid2", "khaki"))+ labs(title = "Grouped by Household Income")+ theme(legend.position="bottom")+ theme(axis.text.x = element_text(size=5))+ labs(x = "Vignette ID - Ordered from Most to Least Objectively Stressful", y = "Subjective Stress")

v_domain %>% arrange(desc(severity)) %>%
  select(ID,Score,vignette,Household_income,Relationship,Loneliness) %>%
  pivot_wider(names_from = vignette, values_from = Score) %>%
  ggparcoord(columns = (5:60),scale = "globalminmax", alphaLines = 0.5, groupColumn = "Loneliness",splineFactor = 10) + 
  scale_color_manual(values = c("cadetblue3", "mediumorchid2", "khaki"))+ labs(title = "Grouped by Lonliness")+ theme(legend.position="bottom")+ theme(axis.text.x = element_text(size=5))+ labs(x = "Vignette ID - Ordered from Most to Least Objectively Stressful", y = "Subjective Stress")

v_domain %>% arrange(desc(severity)) %>%
  select(ID,Score,vignette,Household_income,Relationship,sex_assignment) %>%
  pivot_wider(names_from = vignette, values_from = Score) %>%
  ggparcoord(columns = (5:60),scale = "globalminmax", alphaLines = 0.5,groupColumn = "Relationship",splineFactor = 10) + 
  scale_color_manual(values = c("cadetblue3", "mediumorchid2", "khaki"))+ labs(title = "Relationship with Close Ones")+ theme(legend.position="bottom")+ theme(axis.text.x = element_text(size=5))+ labs(x = "Vignette ID - Ordered from Most to Least Objectively Stressful", y = "Subjective Stress")

```

One main takeaway from these visualizations is that vignettes objectively coded as more stressful (those on the left) incited higher subjective stress reactions than those objectively coded as less stressful (those on the right) We found less interesting trends along individual difference factors than expected. The only noticable clustering pattern we see is the one with *sex assignment*. It shows that males are more likely to state that they are less responsive than women in those vignettes with higher objective stress. And overall, females present more subjective stress than males. Other three fatcors present no evident impact on people's subjective ratings. This is interesting in it's own right, as psychological theory would predict that lower income people are consistently more reactive, that lonely people would be consistently more reactive, and that those with more close relationships would be less reactive. 

## Subjective Stress in the 1st Versus 2nd Session and the Relation Between Number of Siblings and Subjective Stress

An old area of psychological research associates birth order with stress reactivity. Although not an active area of research before, early findings suggested that those with more siblings should be generally less stress reactive than those with few siblings. To reinvigorate these areas of study, we investigated how the number of siblings may affect students' stress levels in different life domains Since we have less than five percent of people with 4 or more siblings, we decided to conclude the data based on four categories, each with "0", "1","2","3+" siblings. Finally, these are confimed to be color-blind accessible using our self-generated palette. 

```{r}
#Read in fresh datafiles
subj <- readRDS("Data/vignette_dat.RDS") #read in subjective stress ratings
el <- which(subj$ID == 130) #eliminate duplicate participants
subj <- subj[-el,]
obj <- read.csv("Data/objective codes.csv") #read in objective stress codes
obj <- obj[,c(1,3,4,9)]
colnames(obj) <- c("vid","broad","domain","severity") #relabel
regexp <- "[[:digit:]]+"
subj$vid <- as.numeric(str_extract(subj$vignette, regexp)) #label vignette id's

#Merge everything together
subj <- merge(x = subj, y = obj, by = "vid", all.x = TRUE)
subj <- merge(x = subj, y = Baseline, by.x = "ID",by.y="sid", all.x = TRUE)
subj <- subj[,c(1,2,3,4,5,6,7,8,189)] #subset to variables of interest
subj$sibling_age <- tolower(subj$sibling_age)
subj["sibling_count"] <- 0

#Count up number of siblings
subj$sibling_count <- str_count(subj$sibling_age, '\\d+')
subj$sibling_count<-ifelse(grepl('me', subj$sibling_age),subj$sibling_count-1,subj$sibling_count) #substract 'me','only child' as 1
subj$sibling_count<-ifelse(grepl('only child', subj$sibling_age),0,subj$sibling_count)

#Label Life Domains
subj$domain[subj$domain == 1] <- "Interpersonal Tension"
subj$domain[subj$domain == 2] <- "Work/Education"
subj$domain[subj$domain == 3] <- "Home"
subj$domain[subj$domain == 4] <- "Finances"
subj$domain[subj$domain == 5] <- "Health/Accident"
subj$domain[subj$domain == 6] <- "Discrimination"
subj$domain[subj$domain == 7] <- "Misc"

#Count up number of siblings
subj$score <- as.numeric(subj$score)
subj <- subj[!is.na(subj$domain),]
subj <- subj[!is.na(subj$score),]
subj$sibling_count[is.na(subj$sibling_count)] <- 0
subj["sibnum"] <- ""
subj$sibnum<-ifelse(subj$sibling_count==0,"0",subj$sibnum)
subj$sibnum<-ifelse(subj$sibling_count==1,"1",subj$sibnum)
subj$sibnum<-ifelse(subj$sibling_count==2,"2",subj$sibnum)
subj$sibnum<-ifelse(subj$sibling_count>=3,"3+",subj$sibnum)

#Reformat to be in necessary data structure for ggplot
temp = subj %>% group_by(domain,Session,sibnum)%>% mutate(Score = mean(score))

ggplot(temp, aes(x=factor(sibnum),y=Score,group=Session,colour=Session))+
  geom_point()+
  geom_line()+
  facet_wrap(~domain)+
  xlab("Number of Siblings")+
  ylab("Subjective Stress")+
  scale_color_manual(values=c("cadetblue3", "mediumorchid2"))+
  ggtitle("Subjective Stress vs. Number of Slibings, faceted by Life Categories")+
  theme(legend.position="bottom")


```

Based on this graph, we could a few really interesting foundings:

Overall, we could observe a slight drop of stress level from Session 1 to Session 2, which may be caused by the time periods when the surveys were conducted. We also see an overall trend, where there is an increase of subjective stress when the the number of siblings increases from "1" to "2", and then an relatively bigger decline of subjective stress for students with 3+ siblings, especially on categories such that *Discrimination* and *Interpersonal Tension*. We suspect the reason behind this trend may be that students with more siblings receive less expectations from their parents, and they receive more love , support and care from all of their family members, where do not need to worry about finding new friends and they are more comfortable with themselves and less conscious of their beings. 

For scenarios with *Discrimination* problems, when number of siblings increase to 3 and more, we can see an apparent tendency that people start to feel less stress. We suspect that it may cause by the shared consciousness and understanding we own with more siblings.

For scenarios with *Interpersonal Tension* problem, we can see an extreme decline in the level of subjective stress when the number of siblings is more than 3. We suspect that this is due to the fact that students with more siblings may know better on how to communicate and negotiate with their friends since they have had their "practice" with their siblings, so they feel less stressed about it.

For scenarios with *Finances* problems, we thought there will be large increase of stress level for people have more siblings due to more family burden. However, there is actually a drop of stress level, especially for session 2. 

For scenarios with *Health/Accident* problems, we can see a clear decrease of stress level for both sessions when people have more siblings. We suspect that maybe this is because when you have more siblings, there will be more people care about your health problems and help you overcome any accidents, thus making people feel less stress.


## Potential Vignettes Outliers

We were also interested in visualizing the distribution of responses to the two questions asked for each scenario: 'have you experienced something like this before?' (1=yes) and 'was it easy to imagine yourself in this scenario?' (1=yes). We therefore calculated the proportion of participants who responded yes to each question and visualized a box and whisker plot of those proportions. We chose box and whisker plots because we are interested in finding outliers; in the next iteration of the study we will likely exclude scenarios that were extreme in terms of describing events that the sample hadn't experienced and being difficult to imagine oneself in the scenario.

```{r, message=FALSE, results = FALSE}
#read in subjective ratings of vignettes
subj <- readRDS("Data/vignette_dat.RDS")

#take out participant 130 because two participant's have that ID...
el <- which(subj$ID == 130)
subj <- subj[-el,]

#create column with just vignette number
regexp <- "[[:digit:]]+" #prepare regular expression
subj$vid <- as.numeric(str_extract(subj$vignette, regexp)) #pull out numeric from the strings 

#change score to character vector
subj$score <- as.numeric(subj$score)

#take out rows with NA
subj <- na.omit(subj)

#separate into first and second session 
subj1 <- subj[which(subj$Session==1),]
subj2 <- subj[which(subj$Session==2),]

#SESSION 1
#subset 
e11 <- subj1[grep("experience_1", subj1$vignette),] #subset down to experience 1 (I have experienced something like this before)
e12 <- subj1[grep("experience_2", subj1$vignette),] #subset down to experience 1 (It was easy to imagine myself in this situation)

# Experienced Something Like This Before
#get proportion yes per vignette
e11.l <- split(e11, e11$vid) #turn to a list
temp <- lapply(e11.l, function(x) sum(x$score)/nrow(x))
e11.prop <- as.data.frame(do.call("rbind", temp)) #turn into a data frame
e11.prop$vid <- as.numeric(names(e11.l)) #add back vignette ID
e11.prop$session <- "Session 1"

# Easy to Imagine Myself in this Situation
e12.l <- split(e12, e12$vid) #turn to a list
temp <- lapply(e12.l, function(x) sum(x$score)/nrow(x))
e12.prop <- as.data.frame(do.call("rbind", temp)) #turn into a data frame
e12.prop$vid <- as.numeric(names(e12.l)) #add back vignette ID
e12.prop$session <- "Session 1"

#SESSION 2
#subset 
e21 <- subj2[grep("experience_1", subj2$vignette),] #subset down to experience 1 (I have experienced something like this before)
e22 <- subj2[grep("experience_2", subj2$vignette),] #subset down to experience 1 (It was easy to imagine myself in this situation)

# Experienced Something Like This Before
#get proportion yes per vignette
e21.l <- split(e21, e21$vid) #turn to a list
temp <- lapply(e21.l, function(x) sum(x$score)/nrow(x))
e21.prop <- as.data.frame(do.call("rbind", temp)) #turn into a data frame
e21.prop$vid <- as.numeric(names(e21.l)) #add back vignette ID
e21.prop$session <- "Session 2"

# Easy to Imagine Myself in this Situation
e22.l <- split(e22, e22$vid) #turn to a list
temp <- lapply(e22.l, function(x) sum(x$score)/nrow(x))
e22.prop <- as.data.frame(do.call("rbind", temp)) #turn into a data frame
e22.prop$vid <- as.numeric(names(e22.l)) #add back vignette ID
e22.prop$session <- "Session 2"

# Combine
e1 <- rbind(e11.prop, e21.prop)
e2 <- rbind(e12.prop, e22.prop)

colnames(e1) <- c("proportion", "vid", "session")
colnames(e2) <- c("proportion", "vid", "session")

#set up code to label the outliers in the box and whisker plot
is_outlier <- function(x) {
  return(x < quantile(x, 0.25) - 1.5 * IQR(x) | x > quantile(x, 0.75) + 1.5 * IQR(x))
}

# Box & Whisker Plots
ggplot(e1, aes(x = session, y = proportion)) + 
  geom_boxplot() +
  coord_flip() +
  geom_text_repel(data = e1[is_outlier(e1$proportion),], aes(session, proportion, label = vid)) +
  ggtitle("Have you experienced something like this before?")+
  theme_classic()

ggplot(e2, aes(x = session, y = proportion)) + 
  geom_boxplot() +
  coord_flip() +
  geom_text_repel(data = e2[is_outlier(e2$proportion),], aes(session, proportion, label = vid)) +
  ggtitle("Was it easy to imagine yourself in this scenario?")+
  theme_classic()

```

These visualizations reveal several important things about the study. First, participants generally indicated that it was easy to imagine themselves in the scenarios (means for both session were above 90%), even though they hadn't necessarily been in situations exactly like them before (means for both sessions around 45%-50%). However, there were a few scenarios that participants found difficult to imagine: scenarios 165 and 48. In the next iteration of the study, we will likely remove these scenarios and replace them with situations that are more commonly experienced by undergraduate students.

<!--chapter:end:05-results.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Interactive component

One of the questions we’re interested in is how our students react to different types of content and what kinds of issues cause them more stress than others. We created two stacked bar charts to illustrate our findings:

<iframe src="resources/total.html" width="800" height="500"></iframe>

Based on our first stacked bar chart *Subjective Stress vs. Life Categories*, there are relatively less vignettes in Health/Accident than other categories, and we could tell that there are more vignettes in categories like *Work/Education*, *Discrimination* and *Misc*, and the survey results in Session 2 indicated an overall lower level of stress comparing to the results from Session 1, which may be effected by external factors such as the time period where our survey were conducted, since we conducted our first survey around the end of October where students seem to have higher level of stress on every categories of content, and when we did our second survey around the beginning of November. We suspect that midterms may have increased their overall level of stress and We will look closer this in the later paragraphs.

It also seems that *Discrimination* and *Finances* categories has a larger percentage of students that have high level of stress, and to confirm our observation, we made the second bar charts *Subjective Stress vs. Life Categories (Percentage)* to capture the distribution of the subjective stress levels in each life category.

<iframe src="resources/percentage.html" width="800" height="500"></iframe>

Since we are interested in the relationship between *Subjective Stress* and *Life Categories*, we decided to sort the data by the most severe stress level and in a descending order. Through this graph, we can clearly see that:

1. For content in regard to *Discrimination* and *Finances*, there are a larger portion of students that feel high level of stress. This founding confirmed our suspisions above and it also makes sense since college students are typically young adults that lack financial literacy and economic stability, and race has always been a sensitive issue that causes stress on people and especially young people.

2. There is a larger portion of students that are indifferent about content (when stress severity = 0) related to *Interpersonal Tension* and *Health/Accident*, which also makes sense, considering that college students are typically in good health and rarely need to worry about complicated working relationships, or any relationships in general, so interpersonal tension and health may be least of their worries, comparing to other issues. However, it surprises me that there is also a larger portion of students that are indifferent about content related to *Discrimination*, which may indicate that some people may be less conscious about issues relating to race, while there are also a large percentage of people that are very conscious about that.

3. Based on our first stacked bar chart *Subjective Stress vs. Life Categories*, we mentioned earlier that the survey results in Session 2 seems to reflect an overall lower level of stress comparing to the results from Session 1. Here, we can find an interesting twist that the position of *Health/Accident* and *Work/Education* swapped when sorting by the percentage of most severe level of subjective stress, which confirmed that our test results were effected by external factors, in our case the time period where our survey were conducted. Since we conducted the results from Session 1 were collected around midterm period, we could see an overall decrease of subjective stress levels in the survey results in Session 2, particularly on the midterm related categories -- *Work/Education*. Therefore, we could see that external events could also cause the fluctuation of stress level.

<!--chapter:end:06-interactive.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Conclusion

Overall, our exploratory and data visualization efforts revealed several critial insights. In our ridge plots, we found a disparity between subjective stress responses to the scenarios and objective coder ratings of the scenarios. We found that these disparities were greatest for the low-end objective stressors and most variable for the mid-range objective stressors. Together, these findings suggest that stress reactivity is a subjective process and that future research should acknowledge it as such. In our mosaic plot, we found some interesting patterns related to the life domain that a stressor falls into, with discrimination events and financial events being the most consensually stressful. Next, our parallel coordinate plots did not reveal too many interesting patterns with repspect to stress reactivity. There was some clustering for gender such that women were generally more stress reactive than men (which aligns with previous research in this area) but no real effects of loneliness, close relationships, or socioeconomic status. Future efforts include running these hypotheses about individual differences into a formal statistical model. Our last static visualization was the box and whisker plot, which revealed some outliers in the proportion of participants that had not experienced something like the stressor before and who found it difficult to imagine themselves in the scenarios. Finally, our interactive plot revealed differences in subjective stress for each life category and how that varies from the first and second session of the study.

We have some limitations with our data in three aspects that we could take into account for future directions: 
1) We only have 157 students complete the survey with valid amount of answers, which might be relatively small. With more data, we will have more accurate output on some visualizations. 
2) The fact that only Columbia undergraduate students took the survey might lead to somewhat bias on individual factors such as income or family backgrounds. 
3) We have relatively large proportions (~25%) of missing data for columns like father education and mother education, which has weakened our analysis on these two factors by certain degree.

We learnt a lot about data visualization tools and methods from this class. By completing this final project, we even learned more about all the concepts and gained better insight into how we can use different types of graphs to conduct analyses on real-world data. We also have a better understanding for utilizing D3.js as well as HTML/CSS to produce interactive data visualization on web pages. All in all, it has been great fun to work out graphs and analysis by using different languages such as R, Python and HTML/JavaScript that we learnt from this EDAV class! :)

<!--chapter:end:07-conclusion.Rmd-->

